### 2017-03-08 chapters/ch2-checkpoint.tex
Write signature dissemination

\item A block of type $\gamma$ is a three-tuple, i.e.
  $$c_{i,j} = (\texttt{h}(b_{i,j}), H(\mathcal{C}_r), p)$$
  where $\mathcal{C}_r$ is the consensus result in round $r$ and $p \in {0,1}$
  which indicates whether $i$ wish to become a promoter in the following
  consensus round.

@@

\item The result of a consensus in round $r$ is a set of CP blocks. Namely,
  $$\mathcal{C}_r = \{ c_{i,j} : \text{agreed by the promoters}\}.$$

@@

\begin{lemma}\label{lem:con_consistent}
  If a node sees a valid $\mathcal{C}_{r-1}$ and another node sees a valid
  $\mathcal{C}'_{r-1}$, then $\mathcal{C}_{r-1} = \mathcal{C}'_{r-1}$.
\end{lemma}
\begin{proof}
  (sketch) $\mathcal{C}_{r-1}$ is signed by at least $N-f$ promoters from round
  $r-1$.
\end{proof}

>>>>

\item A block of type $\gamma$ is a five-tuple, i.e.
  $$c_{i,j} = (\texttt{h}(b_{i,j}), H(\mathcal{C}_r), r, p, s)$$
  where $\mathcal{C}_r$ is the consensus result in round $r$ and $p \in {0,1}$
  which indicates whether $i$ wish to become a promoter in the following
  consensus round, finally $s$ is a signature of the block.

@@

\item The result of a consensus in round $r$ is a set of CP blocks. Namely,
  $$\mathcal{C}_r = (r, \{ c_{i,j} : \text{agreed by the promoters}\}).$$

@@

The consensus result $\mathcal{C}_{r-1}$ does not contain all the signatures of
the promoters. Thus, the signatures must also be disseminated by the promoters.
This can be done in the same way as consensus result dissemination. Nodes must
collect $f + 1$ signatures in order to trust $\mathcal{C}_{r-1}$ because there
is at least one honest node in $f + 1$ nodes. If there is a sufficient number of
signatures on the consensus result, we say it is \emph{valid}.

\begin{lemma}\label{lem:con_consistent}
  If a node sees a valid $\mathcal{C}_{r-1}$ and another node sees a valid
  $\mathcal{C}'_{r-1}$, then $\mathcal{C}_{r-1} = \mathcal{C}'_{r-1}$.
\end{lemma}
\begin{proof}
  $\mathcal{C}_{r-1}$ and $\mathcal{C}'_{r-1}$ are signed by at two groups of $f
  + 1$ promoters (does not have to overlap) from round $r-1$. In both groups, at
  least one node is honest. Thus the consensus result is what is actually
  agreed.
\end{proof}
